Figures

### 2020-02-21 figures/00_maps.Rmd
add reservoir map panel

gg_bathy <- 
  ggplot() + 
    geom_sf(data = st_as_sfc(st_bbox(dt_bathy)), alpha = 1, size = 0.6, 
          color = "black", fill = "#1D9DCF") +
    geom_sf(data = st_crop(states_all, st_as_sfc(st_bbox(dt_bathy))), fill = "gray", color = "black", size = 0.3) +
    geom_sf(data = st_crop(states_focal, st_as_sfc(st_bbox(dt_bathy))), fill = "white", color = "black", size = 0.4) + 
    geom_sf(data = dt_bathy, aes(color = maxdepth_class), 
                    size = 0.2, alpha = 0.8) +
    scale_color_manual(values = viridisLite::viridis(4)) +
    labs(color = "Max depth (m)") +
    coord_sf(xlim = c(-103.81483, -67.10548), ylim = c(37.5, 48.72102)) +
    theme_void()

@@

```{r 00_map_bathy, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=6}
cowplot::plot_grid(gg_bathy, 
                   gg_shapeclass, 
                   ncol = 1)
```

>>>>

gg_bathy <- 
  ggplot() + 
    geom_sf(data = st_as_sfc(st_bbox(dt_bathy)), alpha = 1, size = 0.6, 
          color = "black", fill = "#1D9DCF") +
    geom_sf(data = st_crop(states_all, st_as_sfc(st_bbox(dt_bathy))), fill = "gray", color = "black", size = 0.3) +
    geom_sf(data = st_crop(states_focal, st_as_sfc(st_bbox(dt_bathy))), fill = "white", color = "black", size = 0.4) + 
    geom_sf(data = dt_bathy, aes(color = maxdepth_class), 
                    size = 0.2, alpha = 0.8) +
    scale_color_manual(values = viridisLite::viridis(4)) +
    labs(color = "Max depth (m)  ") +
    coord_sf(xlim = c(-103.81483, -67.10548), ylim = c(37.5, 48.72102)) +
    theme_void()

@@

```{r gg_reservoir, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
dt           <- st_read("../data/gis.gpkg", "dt", quiet = TRUE) %>%
  mutate(lagoslakeid = as.character(lagoslakeid)) %>%
  distinct(lagoslakeid, .keep_all = TRUE)
dt_withres <- read.csv("../data/lagosus_depth_predictors.csv", 
               stringsAsFactors = FALSE) %>%
  dplyr::distinct(lagoslakeid, reservoir_class) %>%
  mutate(lagoslakeid = as.character(lagoslakeid))
dt           <- inner_join(dt, dt_withres) %>%
  arrange(desc(reservoir_class))

gg_reservoir <- 
  ggplot() + 
    geom_sf(data = st_as_sfc(st_bbox(dt_bathy)), alpha = 1, size = 0.6, 
          color = "black", fill = "#1D9DCF") +
    geom_sf(data = st_crop(states_all, st_as_sfc(st_bbox(dt_bathy))), fill = "gray", color = "black", size = 0.3) +
    geom_sf(data = st_crop(states_focal, st_as_sfc(st_bbox(dt_bathy))), fill = "white", color = "black", size = 0.4) + 
    geom_sf(data = dplyr::filter(dt, !is.na(reservoir_class)), 
            aes(color = reservoir_class), size = 0.03, alpha = 0.3) +
    labs(color = "Reservoir class") +
    coord_sf(xlim = c(-103.81483, -67.10548), ylim = c(37.5, 48.72102)) +
    theme_void()

gg_reservoir
```

```{r 00_map_bathy, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=6}
theme_opts <- guides(color = guide_legend(
  override.aes = list(size = 2)))
cowplot::plot_grid(gg_bathy + theme_opts, 
                   gg_shapeclass + theme_opts,
                   gg_reservoir + theme_opts,
                   ncol = 1)
```

### 2020-02-21 manuscript/figures.Rmd
add reservoir map panel

```{r maps_dot_bathy, fig.cap = "Map of lake maximum depth measurements calculated from lake bathymetry surfaces.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/00_map_bathy-1.pdf")
```

>>>>

```{r maps_dot_bathy, fig.cap = "Map of study lakes showing A) lake maximum depth measurements, B) cross-section shape class, and C) reservoir classification.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/00_map_bathy-1.pdf")
```
